The transition redshift as a probe of reionization

### 2019-08-13 paper/ms.tex
Expand detectability section to talk about CDIM

\section{Detectability}
Up to this point, we have not been specific about which galactic emission line
one might consider using to measure \zst{}. This is because computing \zst{}
from our simulations with our simple line intensity model
(\S~\ref{ssec:oiii_int_map}) does not require specifying the total average
intensity of the field.

>>>>

\section{Detectability}
Up to this point, we have not been specific about which galactic emission line
one might consider using to measure \zst{}\,--\,in fact, our entire formalism
could be executed using a galaxy survey, if one with sufficient redshift
accuracy and depth could be executed. While it will not be possible for a
traditional galaxy survey to extend to $z\sim10$ in the near future, it may be
possible to execute a survey of line-emitting galaxies, e.g., with
[\OIII]-emitters \citep{2018MNRAS.481L..84M, 2019arXiv190610863M}.

In this work we will consider the prospect of performing intensity mapping
measurements of the H$\alpha$ line using the proposed, space-based Cosmic Dawn
Intensity Mapper (CDIM) \citep{2019arXiv190303144C}. CDIM is an infrared
telescope with an $83\,\text{cm}$ dish capable of measuring $R=300$ spectra
from wavelengths $0.75\,\mu\text{m}$ to $7.5\,\mu\text{m}$. Therefore, CDIM
will be able to measure the H-$\alpha$ line ($656\,\text{nm}$) from $z=0.14$
to $10.4$ and the H-$\beta$ line ($486\,\text{nm}$) from $z=0.54$ to $14.4$,
so long as there is a detectable signal. We choose to study the H-$\alpha$ and
H-$\beta$ lines since the uncertainty regarding their total intensity at
$z\sim10$ should be less uncertain than for lines that require metal
enrichment such as [\CII], [\OIII], or [\NII], since the total metal
enrichment of the universe is quickly declining at these high $z$
